Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-04-24 pirouette_article.tex

# Create phylogeny
set.seed(314)
phylogeny <- create_exemplary_dd_tree(
  n_taxa = 6, 
  crown_age = 10
)

@@

The DD tree that is generated by this code is as shown in Figure \ref{fig:dd_tree},
which has an arbitrarily chosen crown age of ten time units and six taxa.

>>>>

# Create phylogeny
set.seed(314)
phylogeny <- create_exemplary_dd_tree(
  n_taxa = 6, 
  crown_age = 10,
  extinction_rate = 0.1
)

@@

The DD tree that is generated by this code is as shown in Figure \ref{fig:dd_tree},
which has an arbitrarily chosen crown age of 10 time units and 6 tips for an extinction rate of 0.1. The carrying-capacity is also set at 6. The initial speciation rate $\lambda_0$ is chosen such that the expected number of species in a constant-rate BD model would be equal to the number of tips, which amounts to $\lambda_0 = 0.63$.
